---
title: "Bandwise Analyses"
author: "Matt Kmiecik"
date: last-modified
date-format: iso
format: pdf
execute: 
  freeze: auto
editor: source
editor_options: 
  chunk_output_type: console
---

```{r setup, include=TRUE, warning=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
#knitr chunk options for document ----
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# libraries ----
library(tidyverse)

# custom functions ----
fns <- c("custom_datatable.R", "regenerate_plots.R")
walk(here::here("fns", fns), source) # walk() returns input invisibly

# data ---
f <- here::here("output", "r-analysis", "bandwise-analyses-db.rds")
res <- read_rds(f)

# reconstructs plots ----
plots <- regenerate_plots(results = res, p_fdr = FALSE)
```

## Description

After preprocessing the data in MATLAB, data were brought into R for further visualization. I compared participants' global power estimates across blocks, stimulation type, time (pre vs. post testing), and electrode position. From there, I determined that specific participants' blocks were outliers due to noise that affected the entire montage (mainly from large fluctuations in signal from noisy reference channels.)

## Broadband Power Spectral Density Histogram

```{r}
plots$delta$histogram
```




